%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Founder \& Consultant} % Job title
    {Enacted Services} % Organization
    {Akron, OH} % Location
    {Jul. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and bootstrapped a hardened Linux distribution for a client's Internal Development Platform.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer III (Engineering - Lead)} % Job title
    {Ezurio, Inc.} % Organization
    {Akron, Ohio} % Location
    {Jan. 2023 - Jul. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and implemented Internal Development Platform for cloud adoption and migrated all DevOps workloads to AWS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer III (IT)} % Job title
    {Laird Connectivity, Inc.} % Organization
    {Akron, Ohio} % Location
    {Jul. 2019 - Jan. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded adoption of GitHub Enterprise and Jira Cloud for all development teams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer II (IT)} % Job title
    {Laird Connectivity, Inc.} % Organization
    {Akron, Ohio} % Location
    {Apr. 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed software and processes to perform comprehensive data scrubbing and domain migration for all DevOps systems and datasets as part of divestiture.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer I (IT)} % Job title
    {Laird PLC} % Organization
    {Akron, Ohio} % Location
    {May. 2016 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and implemented a development platform based on Packer, Terraform, Ansible, Docker, and Rancher.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AWS Systems Administrator} % Job title
    {My1HR, Inc.} % Organization
    {Akron, Ohio} % Location
    {Mar. 2013 - Feb. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Primary system administrator responsible for the design, implementation, and security of all IT systems for a small SaaS startup.}
        \item {Provided ongoing management, performance tuning, and cost management for approximately 50 Linux, Unix, and Windows systems in the Amazon Web Services cloud.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Programmer} % Job title
    {Jay Mutter et al.} % Organization
    {Akron, Ohio} % Location
    {Jan. 2012 - Mar. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented multi-platform economic modeling application.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
